Prestige bias in cultural evolutionary dynamics

### 2023-11-15 ms/ms.tex
more revising for rev2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Models}
We begin with a continuous-trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}. Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
We extend this model to include prestige bias and then develop a version of the model with a dichotomous trait to facilitate mathematical analysis.

@@

For simplicity, we use the dichotomous-trait model, which also assumes a constant success-bias weight $\alpha_{i,j}=\alpha$, and we do not include trait estimation error in this analysis, i.e., $e_i=0$.
As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Models}
We begin with a continuous-trait model with indirect success bias, previously suggested by Boyd and Richerson~\citep{evolutionBook}. Note that the indirect success bias is due to an indirect evaluation, in which a certain phenotype is used to evaluate the success of potential role-models.
We extend this model to include prestige bias, which introduces a within-generation model-choice process.
To facilitate mathematical analysis, we also develop a simpler version of the model with a dichotomous trait.

@@

For simplicity, we use the dichotomous-trait model, which also assumes a constant success-bias weight $\alpha_{i,j}=\alpha$, and we do not include trait estimation error in this analysis, i.e., $e_i=0$.
As shown above, transmission in our model is approximately Dirichlet-Multinomial distributed (\Cref{cor:dirichlet} and \cref{eq:copier_choose}).
We focus on two scenarios: the first scenario is of a `constant environment' in which the same phenotype, $\hat{A}$, is always favored by success bias; the second scenario is of a `changing environment' in which the phenotype favored by success bias cycles between the invading phenotype $\hat{A}$ and the resident phenotype $A$ (i.e., $\hat{A}$ starts as the rare phenotype).
